Analyzing the influence of Selection on Genetic Programming's Generalization ability in Symbolic Regression

### 2022-06-26 docs/rmd/presentation/slides.Rmd
autogit

---
title: "Analyzing the influence of Selection on Genetic Programming's Generalization ability in Symbolic Regression"
subtitle: "A comparison of epsilon-lexicase Selection and Tournament Selection"
author: "Roman Hoehn"
affiliation: "Johannes Gutenberg University Mainz"
date: "2022-06-29"
output:
  beamer_presentation:
    #theme: "Darmstadt"
    colortheme: "beaver"
    fonttheme: "structurebold"
    keep_tex: true
    fig_caption: yes
    number_sections: true
    slide_level: 2
toc: yes
toc_depth: 1
bibliography: ../bib/bib/ref.bib
csl: ../bib/csl/harvard1.csl
---

>>>>

---
title: "Analyzing the influence of Selection on Genetic Programming's Generalization ability in Symbolic Regression"
subtitle: "A comparison of epsilon-lexicase Selection and Tournament Selection"
author: "Roman Hoehn"
affiliation: "Johannes Gutenberg University Mainz"
date: "2022-06-29"
output:
  beamer_presentation:
    theme: "Frankfurt"
    #colortheme: "beaver"
    fonttheme: "structurebold"
    keep_tex: true
    fig_caption: yes
    number_sections: true
    slide_level: 2
toc: yes
toc_depth: 1
bibliography: ../bib/bib/ref.bib
csl: ../bib/csl/harvard1.csl
---
